The design of shallow state blockchain

### 2020-05-12 abstract.tex
背景寫一半
更新英文摘要

\bigbreak
\noindent \textbf{關鍵字：}{\, \makeatletter \@keywordszh \makeatother}
\end{abstractzh}

\begin{abstracten}
This thesis presents a benchmark for region of interest (ROI)
detection. ROI detection has many useful applications and many
algorithms have been proposed to automatically detect ROIs.
Unfortunately, due to the lack of benchmarks, these methods were
often tested on small data sets that are not available to others,
making fair comparisons of these methods difficult. Examples from
many fields have shown that repeatable experiments using published
benchmarks are crucial to the fast advancement of the fields. To
fill the gap, this thesis presents our design for a collaborative
game, called Photoshoot, to collect human ROI annotations for
constructing an ROI benchmark. With this game, we have gathered a
large number of annotations and fused them into aggregated ROI
models. We use these models to evaluate five ROI detection
algorithms quantitatively. Furthermore, by using the benchmark as
training data, learning-based ROI detection algorithms become
viable.

\bigbreak
\noindent \textbf{Keywords:}{\, \makeatletter \@keywordsen \makeatother}
\end{abstracten}

>>>>

\bigbreak
\noindent \textbf{關鍵字：區塊鏈、無狀態區塊鏈、快取、資料結構}{\, \makeatletter \@keywordszh \makeatother}
\end{abstractzh}

\begin{abstracten}

Cryptocurrency based on blockchain is a peer to peer trading system. In this decentralized system, each node maintain a complete ledger which records entire transaction history of all account. The system has the characteristics that it is very hard to tamper with the data. However, such characteristic only makes the data increase but do not decrease. Years after years, requirement to single node will get higher and higher. Once some entities get overwhelmed, the degree of centralization of this blockchain system will gradually rise.

Dealing with the issue, stateless blockchain is a promising approach. To be more specific, in this system, each transaction is attached with proof of validity. With this approach, there is no need for a node to access the disk to search past information of the ledger. Instead, node only verifies the proof attached to each transaction. Therefore, it will significantly reduce the space of data storage for each node.

In this paper, we will discuss the following two points.
First, it only need to cache part of information instead of attaching proof to each transaction. It is highly possible to infer the validity of a transaction from other valid transaction appearing recently. Second, when blockchain forks, it have to go back to the bifurcation point and create new cache of new blocks. To reach the purpose, we propose an immutable data structure so that cache can be rapidly computed under any situation. Finally, we conduct the experiments with different workload to understand the performance of different cache strategies and data structures.

\bigbreak
\noindent \textbf{Keywords:blockchain, stateless blockchain, cache, data structure}{\, \makeatletter \@keywordsen \makeatother}
\end{abstracten}
